\bf On semidefinite-representable sets over valuation fields

### 2025-05-20 article/paper_padic_spec.tex
modif abstract

\begin{abstract}
  \noindent
  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
  of linear and semidefinite programming, and form the family of
  semidefinite-representable sets. This paper investigates versions of these sets and of
  the related optimization problems with data over a field $K$ with valuation.
  We prove that basic properties of semidefinite-representable sets generalize to this setting.
  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
  representable over $K$ but are not $K$-spectrahedra.
\end{abstract}

>>>>

\begin{abstract}
  \noindent
  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
  of linear and semidefinite programming, and form the family of
  semidefinite-representable sets. This paper investigates versions of these sets and of
  the related optimization problems with data over a field $K$ with valuation.
  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
  of Smith normal forms.
  We prove that basic properties of semidefinite-representable sets generalize to this setting.
  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
  semidefinite representable over $K$ but are not $K$-spectrahedra.
\end{abstract}
